Geometric variational problems

### 2020-11-11 NSF2020/Description/background.tex

\caption{The exterior domain $\Omega$ is the solvent region surrounding a
number of rigid particles $P_1,$ $P_2,$ $P_3,$ \dots 
The surface $S$ is the solvent-particle interface, indicated by the unit
normal $\mathbf{n}.$ }\label{fig:domain}

@@

To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  modeling
the solvent surrounding a number of particles (Figure \ref{fig:domain}).
The HAP must be an energy of the shape of the region because hydrophobic
attraction is non-additive. The boundary of the region is the
water-particle interface and some parts of this surface are hydrophobic
while others are hydrophilic. Monte Carlo simulations show that water
changes structure at hydrophobic interfaces~\cite{Luzar1987,
Jonsson2006, Varilly2011}. Due to rapid fluctuation in the hydrogen bond
network, restructuring at the interface extends into bulk water. This
motivates the following definition for the HAP of the particles:
\begin{align}
\label{HAP}
  \Phi = \gamma \iiint_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,dx \,dy \,dz, 
\end{align}
where $u$ is the unique solution of the screened Laplace equation boundary value problem 
\begin{equation}
  \label{SL}
  -\rho^2 \Delta u + u = 0, \mbox{ } x \in \Omega, \qquad
  u = f,  \mbox{ } x \in \partial \Omega, \qquad 
  u(x) \to 0 \mbox{ as } |x| \to \infty.
\end{equation}
The scalar function $u(x)$ is called the water activity. Its boundary
values $f$ define the degree of hydrophobicity of the water-particle
interface. If $f=1$, the interface is hydrophobic and water has lost
rotational freedom. Conversely, if $f=0$, the interface has the same
rotational freedom as in bulk water. The parameter $\rho$ is the decay
length of attraction, around 1 nm, and the parameter $\gamma$ is the
interfacial tension~\cite{Israelachvili1954}. Both parameters contain
information about the quality of the solvent~\cite{Discher2002}.

From a phenomenological perspective, equations~\eqref{HAP}
and~\eqref{SL} is an appropriate model of hydrophobic attraction.
Specifically, using boundary layer analysis, it is possible to show that
$\Phi$ converges to a surface energy in the zero-decay length
limit~\cite{Lee2018, Lin2015, Shibata2004}. For non-zero decay lengths,
solutions of~\eqref{SL} yield an attractive interaction between
hydrophobic parallel disks separated by water~\cite{Eriksson1989}. Also,
we have demonstrated with simulation that the forces derived from HAP
theory are non-additive and significantly deviate from a pairwise
potential~\cite{Meyer2006, Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

@@

and energy estimates, any solution of~\eqref{SL} is the minimizer

@@

  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n} \,dS,\quad
  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.

@@

Our previous verifies that this system is force- and torque-free and
\S\ref{subsec:specific_aim_2} addresses the numerical challenges in

@@

supply viscous dissipation, we incorporated the mobility problem in

@@

&-\mu \Delta {\bf u} + \nabla p = 0, \quad \text{in}\ \Omega, \qquad 
\nabla \cdot {\bf u} = 0,  \quad \text{in}\ \Omega,\\
&{\bf u}({\bf x}) \to 0 \quad \text{as}\ |{\bf x}|\to \infty,\qquad 

@@

specifies the fluid velocity at infinity; the fourth equation enforces a
rigid body motion constraint on each particle, where $\mathbf{v}_i$ and
$\boldsymbol{\omega}_i$ are unknown translation and angular velocities
of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of
$P_i$; the last two equations state that the net forces and torques on
each particle are ${\bf F}_i$ and ${\bf T}_i$
from~\eqref{forceandtorque}, respectively, and $\boldsymbol{\sigma}$ is
the fluid shear stress. The time integration of particle configurations
goes as follows: \textbf{(i)} solve the BVP~\eqref{SL} for the screened
Laplace equation, \textbf{(ii)} determine the rigid body forces and
torques~\eqref{forceandtorque}, \textbf{(iii)} solve the Stokes mobility
problem~\eqref{eq:stokes} for rigid body motion, \textbf{(iv)} update
the particle configuration. Numerical challenges and how these
challenges are overcome are described in \S\ref{subsec:specific_aim_2}.

@@

As a proof of concept, our work has already tested for elastic energies
for bending, stretching and tilt of the bilayer assembly. Extracting
coefficients from the HAP simulations showed strikingly positive
agreement with experimentally determined values \cite{Fu2018_SIAM}.
Encouraged by these results and the hydrodynamic simulations of the
bilayer assembly, the PIs propose to further extend the HAP model and
the numerical schemes (see \S\ref{sec:proposed-work}) to make direct
comparison with experiments, the continuum liquid crystal results and MD
simulations results, to establish that the HAP model has the capability
and adaptivity to model phenomena across length scales and time scales.

Over the past decades, researchers have used a number of mathematical
tools to simulate vesicles in a shear flow, including lattice Boltzmann
\cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian dynamics
\cite{NoguchiTakasu2002_BJ}, phase field
\cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, level set
\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral
\cite{Shravan09,Rahimian15} and immersed boundary approaches
\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. Most of
these approaches assume a mathematical surface, whether implicitly or
explicitly, and define an elastic bending energy of the surface. 
%The vesicle obeys fluid
%transport and in turn the fluid balances shear stress with the vesicle's bending force.

Our HAP approach differs from prior methods in a number of respects.
First, we do not assume a surface. Rather, we more fundamentally
consider a collection of amphiphilic particles.  The collection of
amphiphiles minimize hydrophobic interactions by sequestering
hydrophobic tails in the form of a bilayer, and the particles' excess
free energy gives rise to an elastic bilayer energy. The second
difference lies in the fluid-interface coupling. Here, the associated
mobility problem~\eqref{eq:stokes} is more complicated than dealing with
a stress boundary condition or diffusive surface force, because the
fluid velocity must be that of a rigid body motion at the particle
surfaces. The HAP model also addresses the existence of multiple phases.
We can vary lipid length, spontaneous curvature, and bending rigidity by
introducing differentiating particle shapes and hydrophobic boundary
conditions (Figure \ref{fig:demixing}). In contrast, continuum theory
deals with multiple phases through additional surface densities that
must then satisfy specialized transport equations~\cite{Lowengrub07,
MikuckiZhou17}. 
%
\begin{wrapfigure}[17]{l}{0.4\textwidth}
\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
\caption{\label{fig:demixing} An initial assembly of small and 
large particles spontaneous segregates into two smaller bodies. }
\end{wrapfigure}
The greatest strength of using HAP to model lipid bilayer membrane is
the ability to form discontinuities (interfacial singularity) from first
physical principle without any artificial manipulation to rearrangement
the interface.
%The ability to form discontinuities is perhaps the HAP method's greatest strength.
For example, using the HAP model to simulate a vesicle under a shear
flow that is strong enough to cause the vesicle membrane to rupture, we
expect the HAP model to capture the reorganization of lipid molecules on
the scales of membrane thickness ($\sim 5$ nm), which is a nearly
impossible task using phase-field or immerse boundary method without
extreme refinement around the membrane and artificial treatment of
reconnection during the topological change of an interface.

@@

In recent years, researchers have developed a number of numerical methods for calculating
energy minimizing steady equilibrium shapes of lipid bilayer membranes, vesicles and red blood cells.
These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed
boundary method  \cite{Hu,Hu13, KimLai2010_JCP}.
PI RR and collaborators led in part the development of phase field
functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

>>>>

\caption{ \footnotesize The exterior domain $\Omega$ is the solvent
  region surrounding a number of rigid particles $P_1,$ $P_2,$ $P_3,$
  \dots The surface $S$ is the solvent-particle interface, indicated by
  the unit normal $\mathbf{n}.$ }\label{fig:domain}

@@

To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  modeling
the solvent surrounding a number of particles (Figure \ref{fig:domain}).
The HAP must be an energy of the shape of the region because hydrophobic
attraction is non-additive. The boundary of the region is the
water-particle interface and some parts of this surface are hydrophobic
while others are hydrophilic. Monte Carlo simulations show that water
changes structure at hydrophobic interfaces~\cite{Luzar1987,
Jonsson2006, Varilly2011}. Due to rapid fluctuation in the hydrogen bond
network, restructuring at the interface extends into bulk water. This
motivates the following definition for the HAP of the particles:
\begin{align}
\label{HAP}
  \Phi = \gamma \iiint_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,dx \,dy \,dz, 
\end{align}
where $u$ is the unique solution of the screened Laplace equation boundary value problem 
\begin{equation}
  \label{SL}
  -\rho^2 \Delta u + u = 0, \mbox{ } \mathbf{x} \in \Omega, \qquad
  u = f,  \mbox{ } \mathbf{x} \in \partial \Omega, \qquad 
  u(\mathbf{x}) \to 0 \mbox{ as } |\mathbf{x}| \to \infty.
\end{equation}
The scalar function $u(\mathbf{x})$ is called the water activity. Its
boundary values $f$ define the degree of hydrophobicity of the
water-particle interface. If $f=1$, the interface is hydrophobic and
water has lost rotational freedom. Conversely, if $f=0$, the interface
has the same rotational freedom as in bulk water. The parameter $\rho$
is the decay length of attraction, around 1 nm, and the parameter
$\gamma$ is the interfacial tension~\cite{Israelachvili1954}. Both
parameters contain information about the quality of the
solvent~\cite{Discher2002}.

From a phenomenological perspective, equations~\eqref{HAP}
and~\eqref{SL} form an appropriate model of hydrophobic attraction.
Specifically, using boundary layer analysis, it is possible to show that
$\Phi$ converges to a surface energy in the zero-decay length
limit~\cite{Lee2018, Lin2015, Shibata2004}. For non-zero decay lengths,
solutions of~\eqref{SL} yield an attractive interaction between
hydrophobic parallel disks separated by water~\cite{Eriksson1989}. Also,
we have demonstrated with simulation that the forces derived from HAP
theory are non-additive and significantly deviate from a pairwise
potential~\cite{Meyer2006, Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

@@

and energy estimates, the solution of~\eqref{SL} is the minimizer

@@

  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}}
  \cdot \boldsymbol{\nu} \,dS,\quad
  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times
  (\boldsymbol{\sigma}_{\text{hydro}} \cdot \boldsymbol{\nu}) \,dS.

@@

Our previous work verifies that this system is force- and torque-free
and \S\ref{subsec:specific_aim_2} addresses the numerical challenges in

@@

supply viscous dissipation, we incorporate the mobility problem in

@@

  &-\mu \Delta \mathbf{u} + \nabla p = 0, \quad \mathbf{x} \in \Omega, \qquad 
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &{\bf u}(\mathbf{x}) \to 0 \quad \text{as}\ |\mathbf{x}|\to \infty,\qquad 

@@

specifies that the fluid velocity vanishes at infinity; the fourth
equation enforces a rigid body motion on each particle, where
$\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
angular velocities of the $i$-th particle and $\mathbf{a}_i$ is the
center of mass of $P_i$; the last two equations state that the net
forces and torques on each particle are $\mathbf{F}_i$ and
$\mathbf{T}_i$ from~\eqref{forceandtorque}, respectively, and
$\boldsymbol{\sigma}$ is the fluid shear stress. The time integration of
particle configurations goes as follows: \textbf{(i)} solve the
BVP~\eqref{SL} for the screened Laplace equation, \textbf{(ii)}
determine the rigid body forces and torques~\eqref{forceandtorque},
\textbf{(iii)} solve the Stokes mobility problem~\eqref{eq:stokes} for
rigid body motion, \textbf{(iv)} update the particle configuration.
Numerical challenges and how these challenges are overcome are described
in \S\ref{subsec:specific_aim_2}.

@@

As a proof of concept, our work has already tested for elastic energies
for bending, stretching, and tilt of the bilayer assembly. Extracting
coefficients from the HAP simulations shows strikingly positive
agreement with experimentally determined values~\cite{Fu2018_SIAM}.
Encouraged by these results and the hydrodynamic simulations of the
bilayer assembly, the PIs propose to extend the HAP model and the
numerical schemes (see \S\ref{sec:proposed-work}) to make direct
comparison with experiments, the continuum liquid crystal results and MD
simulations results, to establish that the HAP model has the capability
and adaptivity to model phenomena across length scales and time scales.

Over the past decades, researchers have used a number of mathematical
tools to simulate vesicles in a shear flow, including lattice
Boltzmann~\cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian
dynamics~\cite{NoguchiTakasu2002_BJ}, phase
field~\cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, level
set~\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary
integral~\cite{Shravan09,Rahimian15} and immersed boundary
approaches~\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}.
Most of these approaches assume a mathematical surface, whether
implicitly or explicitly, and define an elastic bending energy of the
surface. Researchers have developed a number of numerical methods for
calculating energy minimizing steady equilibrium shapes of lipid bilayer
membranes, vesicles and red blood cells. These approaches range from the
finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, phase
field method~\cite{Du05,QiangDu08,Lowengrub13} to immersed boundary
method~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators led in
part the development of phase field functionals of membrane elastic
energy and approaches to coupling membrane elasticity to
fluids~\cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

%The vesicle obeys fluid
%transport and in turn the fluid balances shear stress with the vesicle's bending force.

Our HAP approach differs from prior methods in a number of respects.
First, we do not assume a surface. Rather, we more fundamentally
consider a collection of amphiphilic particles.  The collection of
amphiphiles minimize hydrophobic interactions by sequestering
hydrophobic tails in the form of a bilayer, and the particles' excess
free energy gives rise to an elastic bilayer energy. The second
difference lies in the fluid-interface coupling. Here, the associated
mobility problem~\eqref{eq:stokes} is more complicated than dealing with
a stress boundary condition or diffusive surface force, because the
fluid velocity must be that of a rigid body motion at the particle
surfaces. The HAP model also addresses the existence of multiple phases.
We can vary lipid length, spontaneous curvature, and bending rigidity by
introducing different particle shapes and hydrophobic boundary
conditions (Figure~\ref{fig:demixing}). In contrast, continuum theory
deals with multiple phases through additional surface densities that
must then satisfy specialized transport equations~\cite{Lowengrub07,
MikuckiZhou17}. 
%
\begin{wrapfigure}[14]{l}{0.35\textwidth}
\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:demixing} \footnotesize An initial assembly of
  small and large particles spontaneously segregates into two smaller
  bodies.}
\end{wrapfigure}
The greatest strength of using HAP to model lipid bilayer membrane is
the ability to form discontinuities (interfacial singularity) from first
physical principles without any artificial manipulation to rearrangement
the interface. For example, using the HAP model to simulate a vesicle
under a shear flow that is strong enough to cause the vesicle membrane
to rupture, we expect the HAP model to capture the reorganization of
lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which
is a nearly impossible task using phase-field or immerse boundary method
without extreme refinement around the membrane and artificial treatment
of reconnection during the topological change of an interface.

@@

### 2020-11-11 NSF2020/Description/broaderimpacts.tex

The proposed mathematical analysis and modeling will provide a
transformative understanding of the collective dynamics of amphiphilic
particles such as (1) their self-assembly into micelles and bilayers, (2) the material properties of such self-assembly, 
and (3) the interaction between these building blocks. Amphiphilic Janus
particles have gained increasing popularity for fabrication of smart
materials. The proposed hybrid continuum model, mathematical analysis
and numerical algorithms will have transformative impact on precision
design for specific mechanical properties of materials made of
amphiphilic nanoparticles. An important component of this proposal is
the interdisciplinary education and training of both undergraduate
students, graduate students, and postdoctoral fellows. The combination
of mathematical modeling, analysis, and scientific computing in this
project provides a compelling example of the importance of mathematics
in biophysics and engineering applications. The concepts and methods
described here go beyond the context of amphiphilic particles and lipid
molecules. They extend to other problems featuring microscopic phase
separation that leads to formation of mesoscopic domains. This situation
arises, for example, in biological development in systems biology. The
methods developed here have the potential to impact those and other
related areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have immediate impact on undergraduate and
graduate education. At the undergraduate level, the project will involve
and support undergraduate researcher from Fordham University. The
supported summer researchers will gain valuable first-hand experience in
inherently interdisciplinary, mathematical fluid modeling and
computation. We will incorporate research into teaching, especially in
differential equation and programming courses. PI YNY will work on simple modeling of self-assembly problems 
with both undergraduate and high school students from Newark Science Park High School. 
PI YNY has a track record of working with local high school students for their research projects before they apply for colleges.
PI BQ will expose
undergraduate and high school students to the reserach through the
Undergraduate Research Opportunity Program (UROP) and Young Scholar's
Program (YSP).

Over the past eight years, PI RR has included many undergraduates in
the execution of research initiatives, coauthoring publications. He has
a track record for supporting underrepresented groups, being called on
by the Collegiate Science and Technology Entry Program (CSTEP) to make
opportunities for promising students, for example. He has mentored two
Clare Boothe Luce Scholars, one a U.S. Marine Corp veteran, and a high
school student in the NYU GSTEM program.

The PIs will capitalize on the synergy between both FSU's doctoral program in Scientific Computing and NJIT's doctoral programs
in Mathematical Sciences and Fordham's undergraduate focus in the
Department of Mathematics. Promising, young undergraduate scientists
from the Bronx community while find a natural pipeline into graduate
studies through working directly or indirectly on this project. On the
graduate-level education, PI YNY expects to train and
support a PhD student for
two more years. 
%Yuexin Liu has past experiences in the undergraduate training program at NJIT, and will train an undergraduate intern. 
The PIs will foster vertical integration between the senior personnel, their
collaborators, postdocs, doctoral and Bachelor students, enhancing the
learning environment.
%

@@

\section{Intellectual Merit}
A central theme of the project is the mathematical development and
analysis of the physical model for interaction between many amphiphilic
particles. The model formulates the interaction potential through a
screened Laplace equation boundary value problem possessing the physical
properties like non-additivity and decay of realistic hydrophobic
attraction. Colloidal systems collectively self-assemble into bilayer
morphologies, and we analyze the elastic properties of these amphiphilic
particle ensembles. This allows us to interpret the Helfrich free
energy in terms of hydrophobic interactions and specific molecular
characteristics. We extend the capabilities of the boundary integral
equation quadrature by expansion method to perform large particle number
simulations in three dimensions with collisions. Results from these
computations will be used to compare collective amphiphilic against
experiment, and study the optimal design of three-dimensional
functional materials.

>>>>

The proposed mathematical analysis, modeling, and numerical algorithms
will transform our understanding of the collective dynamics of
amphiphilic particles such as (1) their self-assembly into micelles and
bilayers, (2) the material properties of such self-assembly, and (3) the
interaction between these building blocks. In addition to biophysical
applications, amphiphilic Janus particles have recently popularity for
fabrication of smart materials. The proposed work will have a
transformative impact on precision design for specific mechanical
properties of materials made of amphiphilic nanoparticles. An important
component of this proposal is the interdisciplinary education and
training of both undergraduate students, graduate students, and
postdoctoral fellows. The combination of mathematical modeling,
analysis, and scientific computing in this project provides a compelling
example of the importance of mathematics in biophysics and engineering
applications. The concepts and methods described here go beyond the
context of amphiphilic particles and lipid molecules. They extend to
other problems featuring microscopic phase separation that leads to
formation of mesoscopic domains. This situation arises, for example, in
biological development in systems biology. The methods developed here
have the potential to impact those and other related areas in
biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have immediate impact on undergraduate and
graduate education. At the undergraduate level, the project will involve
and support undergraduate researcher from Fordham University. The
supported summer researchers will gain valuable first-hand
interdisciplinary experience in mathematical fluid modeling and
computation. We will incorporate research into teaching, especially in
differential equation and programming courses. PI YNY will work on
simple modeling of self-assembly problems with both undergraduate and
high school students from Newark Science Park High School. PI YNY has a
track record of working with local high school students for their
research projects before they apply for colleges. PI BQ will work with
undergraduate and high school students through the Undergraduate
Research Opportunity Program (UROP) and Young Scholar's Program (YSP) as
he has done in the past.

Over the past eight years, PI RR has included many undergraduates in the
execution of research initiatives and coauthoring publications. He has a
track record for supporting underrepresented groups, being called on by
the Collegiate Science and Technology Entry Program (CSTEP) to make
opportunities for promising students, for example. He has mentored two
Clare Boothe Luce Scholars, one a U.S.~Marine Corp veteran, and a high
school student in the NYU GSTEM program.

The PIs will capitalize on the synergy between both FSU's doctoral program in Scientific Computing and NJIT's doctoral programs
in Mathematical Sciences and Fordham's undergraduate focus in the
Department of Mathematics. Promising, young undergraduate scientists
from the Bronx community will find a natural pipeline into graduate
studies by working directly or indirectly on this project. On the
graduate-level education, PI YNY expects to train and support a PhD
student for two more years. PI BQ will advise a postdoctoral fellow for
two years. The PIs will foster vertical integration between the senior
personnel, their collaborators, postdocs, doctoral, and Bachelor
students, enhancing the learning environment.

@@

\section{Intellectual Merit}
A central theme of the project is the mathematical development and
analysis of the physical model for interaction between many amphiphilic
particles. The model formulates the interaction potential through a
screened Laplace equation boundary value problem possessing the physical
properties like non-additivity and decay of realistic hydrophobic
attraction. Colloidal systems collectively self-assemble into bilayer
morphologies, and we analyze the elastic properties of these amphiphilic
particle ensembles. This allows us to interpret the Helfrich free energy
in terms of hydrophobic interactions and specific molecular
characteristics. We extend the capabilities of the boundary integral
equation and time stepping methods to stably perform large particle
number simulations in three dimensions. Results from these computations
will be used to compare collective amphiphilic against experiment, and
study the optimal design of three-dimensional functional materials.
